%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {Persistent Systems}{Apr 2024 -- Present}
   {\hspace{1mm} \textit{Data engineering Lead | Databricks, Pyspark, Dremio, ADF, ADLS}}{Pune, India}
    \resumeItemListStart
    \vspace{0.1cm}
        \resumeItem{Employed Databricks to transform raw data into structured formats, creating Delta tables and views for enhanced data accessibility.}
        \smallskip
        \resumeItem{Enabled end-users to interact with transformed data through the Dremio application, facilitating streamlined data analysis and reporting.}
        % \smallskip
    \resumeItemListEnd

\resumeSubHeadingListEnd
% PWC-US PriceWaterhouse Coopers
\resumeSubHeadingListStart

    \resumeSubheading
    {PriceWaterhouseCoopers (PwC) - US}{Nov 2021 -- Mar 2024}
    {\hspace{1mm} \textit{Senior Associate Data Engineer | Python, Pyspark, Databricks, Airflow, PostgreSQL, GraphQL}}{Bangalore, India}
     \resumeItemListStart
     \vspace{0.1cm}
         \resumeItem{Developed and maintained data processing pipelines in Airflow(Python) using Azure Data Lake and Delta
         Table through Azure Databricks(PySpark/Pandas).}
         \smallskip
         \resumeItem{Utilized Azure Event Hub to efficiently collect and process data streams from other microservices.}
         % \smallskip
 
     \resumeItemListEnd
    \vspace{0.1cm}
   {\hspace{1mm} \textit{Associate Data Engineer II| Python, Pyspark, FastAPI, Airflow, PostgreSQL, GraphQL}}
    \resumeItemListStart
    % \vspace{0.1cm}
        \resumeItem{Designed and implemented \textbf{Restful APIs} for managing metadata.}
        \smallskip
        \resumeItem{Implemented GraphQL queries and mutations for data manipulation through Airflow.}
        \smallskip
        \resumeItem{Collaborated with stakeholders to gather project requirements, define data engineering best practices, and
        ensure successful project delivery.}
        % \smallskip
    \resumeItemListEnd
\resumeSubHeadingListEnd
% Accenture
\resumeSubHeadingListStart

    \resumeSubheading
    {Accenture}{Nov 2019 -- Nov 2021}
   {\hspace{1mm} \textit{Application Development Analyst | Python, Pandas, FastAPI, React, PyTest}}{Mumbai, India}
    \resumeItemListStart
    \vspace{0.1cm}
        \resumeItem{Developed a web-based low code/no code tool using Python and React for RPA component integration and orchestration.}
        \smallskip
        
        \resumeItem{Conducted data mining on loan and insurance-related documents using regex and string manipulation
        techniques, collaborating with business analysis teams to identify and extract fields of interest.}
        % \smallskip
        
    \resumeItemListEnd
    \vspace{0.1cm}
    {\hspace{1mm} \textit{Associate Software Engineer | Python, Pandas, PyTest, SQL }}
    \resumeItemListStart
    % \vspace{0.1cm}
        \resumeItem{Designed and implemented a Python script for extracting and cleaning field data from PDF and text documents using before-after pattern matching.}
        \smallskip
        \resumeItem{Achieved a \textbf{reduction} of over \textbf{80\%} in developer time by automating daily data extraction tasks using Python scripts.}
        % \smallskip
    \resumeItemListEnd
\resumeSubHeadingListEnd